\documentclass[14pt,ignorenonframetext,]{beamer}
\usetheme{Warsaw}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifxetex
  \usepackage{fontspec,xltxtra,xunicode}
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
\else
  \ifluatex
    \usepackage{fontspec}
    \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \else
    \usepackage[utf8]{inputenc}
  \fi
\fi
% Comment these out if you don't want a slide with just the
% part/section/subsection/subsubsection title:
\AtBeginPart{\frame{\partpage}}
\AtBeginSection{\frame{\sectionpage}}
\AtBeginSubsection{\frame{\subsectionpage}}
\AtBeginSubsubsection{\frame{\subsubsectionpage}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\title{Learning by Doing\\{}A Short Introduction to git}
\author{Jianwen WEI}
\date{\today}
\institute[SJTU]{
	School of Electronic Information and Electrical Engineering \\ 
	Shanghai Jiaotong University \\ 
	Shanghai 200240, China
}

\begin{document}
\frame{\titlepage}

\begin{frame}\frametitle{What is Version Control System?}

\end{frame}

\begin{frame}\frametitle{Why we need a VCS?}

\end{frame}

\begin{frame}\frametitle{VCS Work Flow Categories}

\begin{itemize}
\item
  Centralized: {[}VSS{]}{[}{]}, {[}CVS{]}{[}{]},
  {[}Subversion(svn){]}{[}{]}
\item
  Distributed (centralized workflow is also supported here) :
  {[}BitKeeper{]}{[}{]}, {[}git{]}{[}{]}, {[}mercurial{]}{[}{]},
  \ldots{}
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Why git is better than Subversion}

\begin{itemize}
\item
  git is super fast
\item
  Full repository clone
\item
  Local history: you don't need to connect to the server when viewing
  the commit history
\item
  github: social coding
\item
  Other things: better compression, multi workflow support, \ldots{}
\end{itemize}
\end{frame}

\begin{frame}\frametitle{General Advice on Learning git}

\begin{itemize}
\item
  Try git and github
\item
  Most graphical tool/plugsins \emph{SUCK}. Please use the command-line
  git.
\item
  Read git's prompts, run \textbf{git help} to get help.
\item
  Find ``how-to'' on Google, StackOverflow, git book.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{Rules of Thumb for git}

\begin{itemize}
\item
  ``A clear development workflow is worth a bunch of version control
  systems.''
\item
  Modular design, avoid simultaneous source file editing by different
  members.
\item
  Head (latest) version at the master branch is always ready to deploy.
\item
  Modification is made on branches, then merged into master.
\item
  Stay on your own branch.
\item
  Do NOT edit files in .git directory unless you know exactly what you
  are doing.
\end{itemize}
\end{frame}

\begin{frame}\frametitle{git workflow on a stand-alone computer}

\end{frame}

\begin{frame}\frametitle{git workflow with a central repo}

\end{frame}

\begin{frame}\frametitle{gti workflow with multi repos}

\end{frame}

\begin{frame}\frametitle{git command}

\begin{itemize}
\item
  init
\item
  add
\item
  commit
\item
  tag
\item
  branch
\item
  submodule
\item
  Oh, there is a conflict!!!
\item
  ``Time Machine'': stash, stash list, checkout to a commit, checkout to
  master
\end{itemize}
\begin{block}{git command: \emph{init}}

\begin{itemize}
\item
  init
\item
  add
\item
  commit
\end{itemize}
\end{block}

\end{frame}

\begin{frame}\frametitle{Exercise: git environment}

\end{frame}

\begin{frame}\frametitle{Exercise: git local repo}

\end{frame}

\begin{frame}\frametitle{Exercise: diff}

\end{frame}

\begin{frame}\frametitle{Exercise: branch}

\end{frame}

\begin{frame}\frametitle{Exercise: github}

\end{frame}

\begin{frame}\frametitle{Exercise: Remote Branch}

\end{frame}

\begin{frame}\frametitle{Exercise: Conflicts}

\end{frame}

\begin{frame}\frametitle{Exercise: tag}

\end{frame}

\begin{frame}\frametitle{Exercise: Time Machine}

\end{frame}

\end{document}
